---
title: "Understanding Moves Toward Immigration Populism"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(rstanarm)

# Consider someone whose att_end at the end of the experiment is 1 or more units
# greater than their att_start. They become more conservative on immigration
# issues. Consider such people to have made a meaningful move toward immigration
# populism. Let's use `move_to_pop` as a new variable, defined as TRUE for such
# people. We are interested to see if two variables might be associated with
# move_to_pop: treatment and age.

x <- trains %>% 
  mutate(move_to_pop = ifelse(att_end >= att_start + 1, TRUE, FALSE)) %>% 
  select(move_to_pop, treatment, age)


```



How much does being exposed to spanish speakers cause one to be more conservative?(depends on what we are trying to draw an infrence)
wisdom

data - experiment with different people's attitudes - either exposed or not exposed to Spanish speakers 
validity - our data relates to the question we are asking (outcome measure should accurately reflect the phenomenon of interest)
population - 
and ethics.



what is the probability causal effect for treatment to become more populist (for boston)

- two potential outcomes: 1) move_to_pop = true, 2 move_to_pop = false

posterior epred (expectations, expected value, or average, or long term populaiton)
handful of individuals, 10 random indivuals  (posterior predict)

```{r}
fit_1 <- stan_glm(data = x,
                  formula = move_to_pop ~ treatment,
                  family = binomial,
                  refresh = 0,
                  seed = 9)
```
left thing i am trying to understand, right thing is the thing that helps me understand. 


median treatment(control) = posterior for that
the posterior for B1 is centered around -.7 and the .4 SD means the 95% conf inverval must be above and below so -1.1 and -.3

```{r}

newobs <- tibble(treatment = c("Treated", "Control"))

posterior_epred(fit_1, newdata = newobs) %>% 
  as_tibble() %>% 
  mutate(ate = `1` - `2`) %>% 

# 1 is the estimates for probability for someone given control they would become more populist, posterior distributions for the expected value/probability that smeone becomes more populist given that they are in control. the value for treatment minus control (2.9 distrbutions and draws, 5.1 posterior, chapter 8)

   ggplot(aes(x = ate)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
   labs(title = "Posterior for Proportion of populists among those Treated",
         subtitle = "There is about 25% ",
         x = "Probability",
         y = "Probability",
         caption = "Data source: NHANES") +

```


```{r}
newobs <- tibble(treatment = c(rep("Treated", 25)))

# we want the function to be exactly like the data in our data - treated

pp <- posterior_predict(fit_1, 
                        newdata = newobs) %>%
    as_tibble() %>%
    mutate_all(as.numeric) %>% 
  rowwise() %>% 
  mutate(total = sum(c_across()))
 

# for the first 25 people, the first row, how many of them became more populist
# PE is probabilities and PP is p

```

epred if for whole population
predict is for individual people
the next 25 people
some percentage number for the entire population
binomial case looks different from the normal linear model
prediction epred for the average for binomial model is 0 or 1
overall average for a whole population is never zero or one 

assign treatment to 25 people, and see if that changed their attitude
this is a model we made, estimated posterior is not the same as the true posterior

```{r}
pp %>% 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) 
```

